Repeatability Test

### 2017-06-16 pt_characterization/rep_check/u_s_time.tex
Updated Draft for June 16

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC104]{
		\includegraphics[scale=0.43]{u_s_time/104_sec_ut_hist.eps}
		\label{fig:inc104_ut_hist}
	}
	\subfigure[User time frequency on INC112]{
		\includegraphics[scale=0.43]{u_s_time/112_sec_ut_hist.eps}
		\label{fig:inc112_ut_hist}
	}
	\subfigure[User time frequency on INC120]{
		\includegraphics[scale=0.43]{u_s_time/120_sec_ut_hist.eps}
		\label{fig:inc120_ut_hist}
	}
	\subfigure[User time frequency on INC128]{
		\includegraphics[scale=0.43]{u_s_time/128_sec_ut_hist2.eps}
		\label{fig:inc128_ut_hist2}
	}
	\caption{User Time Histograms of INC104 and INC128~\label{fig:ut_hist5}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC160]{
		\includegraphics[scale=0.43]{u_s_time/160_sec_ut_hist.eps}
		\label{fig:inc160_ut_hist}
	}
	\subfigure[User time frequency on INC192]{
		\includegraphics[scale=0.43]{u_s_time/192_sec_ut_hist.eps}
		\label{fig:inc192_ut_hist}
	}
	\subfigure[User time frequency on INC224]{
		\includegraphics[scale=0.43]{u_s_time/224_sec_ut_hist.eps}
		\label{fig:inc224_ut_hist}
	}
	\subfigure[User time frequency on INC256]{
		\includegraphics[scale=0.43]{u_s_time/256_sec_ut_hist2.eps}
		\label{fig:inc256_ut_hist}
	}
	\caption{User Time Histograms of INC160 ... INC256~\label{fig:ut_hist6}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC512 (with one extreme outlier of 513,259 msec removed)]{
		\includegraphics[scale=0.43]{u_s_time/512_sec_ut_hist.eps}
		\label{fig:inc512_ut_hist}
	}
	\subfigure[User time frequency on INC1024]{
		\includegraphics[scale=0.43]{u_s_time/1024_sec_ut_hist.eps}
		\label{fig:inc1024_ut_hist}
	}
	\subfigure[User time frequency on INC2048]{
		\includegraphics[scale=0.43]{u_s_time/2048_sec_ut_hist.eps}
		\label{fig:inc2048_ut_hist}
	}
	\subfigure[User time frequency on INC4096]{
		\includegraphics[scale=0.43]{u_s_time/4096_sec_ut_hist.eps}
		\label{fig:inc4096_ut_hist}
	}
	\caption{User Time Histograms of INC512 ... INC4096~\label{fig:ut_hist7}}
\end{figure}

>>>>

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC104]{
		\includegraphics[scale=0.43]{u_s_time/104_sec_ut_hist.eps}
		\label{fig:inc104_ut_hist}
	}
	\subfigure[User time frequency on INC112]{
		\includegraphics[scale=0.43]{u_s_time/112_sec_ut_hist.eps}
		\label{fig:inc112_ut_hist}
	}
	\subfigure[User time frequency on INC120 with bin size = 1 ms]{
		\includegraphics[scale=0.43]{u_s_time/120_sec_ut_hist1.eps}
		\label{fig:inc120_ut_hist1}
	}
	\subfigure[User time frequency on INC120 with bin size = 2 ms]{
		\includegraphics[scale=0.43]{u_s_time/120_sec_ut_hist.eps}
		\label{fig:inc120_ut_hist}
	}
	\caption{User Time Histograms of INC104 and INC120~\label{fig:ut_hist5}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC128]{
		\includegraphics[scale=0.43]{u_s_time/128_sec_ut_hist2.eps}
		\label{fig:inc128_ut_hist2}
	}
	\subfigure[User time frequency on INC160]{
		\includegraphics[scale=0.43]{u_s_time/160_sec_ut_hist.eps}
		\label{fig:inc160_ut_hist}
	}
	\subfigure[User time frequency on INC192]{
		\includegraphics[scale=0.43]{u_s_time/192_sec_ut_hist.eps}
		\label{fig:inc192_ut_hist}
	}
	\subfigure[User time frequency on INC224]{
		\includegraphics[scale=0.43]{u_s_time/224_sec_ut_hist.eps}
		\label{fig:inc224_ut_hist}
	}
	\caption{User Time Histograms of INC160 ... INC224~\label{fig:ut_hist6}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC256]{
		\includegraphics[scale=0.43]{u_s_time/256_sec_ut_hist2.eps}
		\label{fig:inc256_ut_hist}
	}
	\subfigure[User time frequency on INC512 (with one extreme outlier of 513,259 msec removed)]{
		\includegraphics[scale=0.43]{u_s_time/512_sec_ut_hist.eps}
		\label{fig:inc512_ut_hist}
	}
	\subfigure[User time frequency on INC1024]{
		\includegraphics[scale=0.43]{u_s_time/1024_sec_ut_hist.eps}
		\label{fig:inc1024_ut_hist}
	}
	\caption{User Time Histograms of INC256 ... INC1024~\label{fig:ut_hist7}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[User time frequency on INC2048]{
		\includegraphics[scale=0.43]{u_s_time/2048_sec_ut_hist.eps}
		\label{fig:inc2048_ut_hist}
	}
	\subfigure[User time frequency on INC4096]{
		\includegraphics[scale=0.43]{u_s_time/4096_sec_ut_hist.eps}
		\label{fig:inc4096_ut_hist}
	}
	\caption{User Time Histograms of INC512 ... INC4096~\label{fig:ut_hist8}}
\end{figure}
